---
title: "statcomp"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{statcomp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
pacman::p_load(statcomp,
               tidyverse,
               here,
               tidytuesdayR,
               ggplot2)
```

## Exp(x,k)
This function approximates the exp(x) function from base R as _k_ increases.

```{r}
# Taylor series expansion
Exp(5, k = 1)
Exp(5, k = 10)
Exp(5, k = 100)

# compared to 
exp(5)
```

## calculate_CI()
We will demonstrate how to using this function to create a confidence interval using a Chopped TV show dataset from TidyTuesday. 

```{r, include = FALSE}
# tests if a directory named "data" exists locally
if(!dir.exists(here("data"))) { dir.create(here("data")) }

# saves data only once (not each time you knit a R Markdown)
if(!file.exists(here("data","chopped.RDS"))) {
  url_tsv <- 'https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-25/chopped.tsv'
  chopped <- readr::read_tsv(url_tsv)
  
  # save the file to RDS objects
  saveRDS(chopped, file= here("data","chopped.RDS"))
}
```

1. Data cleaning: read the data and clean, searching for episodes that specifically mention Halloween.
```{r}
chopped <- readRDS(here("data", "chopped.RDS")) # read in .RDS dataset

chopped_clean <- as_tibble(chopped) %>%                 # convert to tibble
        drop_na(c(episode_notes, episode_rating)) %>%   # remove NA
        select(c(episode_notes, episode_rating)) %>%    # select columns
        mutate(has_halloween_theme =
                       grepl("halloween", 
                             episode_notes,
                             ignore.case = TRUE))       # add column has_halloween_theme

```

2. Boxplots of distribution of ratings
```{r}
chopped_clean$has_halloween_theme <- chopped_clean$has_halloween_theme %>% 
        factor(levels = c("FALSE", "TRUE"), 
               labels = c("Normal", "Halloween"))

chopped_clean %>% 
        ggplot() +
        geom_boxplot(aes(y = episode_rating, x = has_halloween_theme)) +
        geom_jitter(aes(y = episode_rating, x = has_halloween_theme), 
                    width = 0.05,
                    alpha = 0.5) +
        theme_minimal() +
        labs(title = "Chopped: episode ratings by theme",
             caption = "Data source: tidytuesdayR",
             y = "Rating",
             x = "Episode theme")
```

3. Calculate 90% confidence interval
```{r}
not_halloween <- chopped_clean %>% 
        dplyr::filter(has_halloween_theme == "Normal") %>%      # filter regular episodes
        select("episode_rating") %>%                            # select episode_rating
        deframe() %>%                                           # make into double
        make_p3_class() %>%                                     # make p3_class
        calculate_CI.p3_class(conf = 0.9)                       # calculate CI

halloween <- chopped_clean %>% 
        dplyr::filter(has_halloween_theme == "Halloween") %>% 
        select("episode_rating") %>% 
        deframe() %>% 
        make_p3_class() %>% 
        calculate_CI.p3_class(conf = 0.9)

not_halloween
halloween

```

Based on the boxplot and confidence intervals, Halloween-themed Chopped episodes were about as popular as regular episodes. The median rating is around 8.5 for both but Halloween-theme episodes were more skewed.
